Daily goals

### 2020-07-02 _TODO.Rmd
kinsey comment pipelines

>>>>

- [ ] Kinsey comment: reduce paragraph about history of pipelines and how they were developed, maybe send to discussion?
  She suggests deleting the whole paragraph and just citing the pipelines at the beginning of L72
  Focus on importance of pipelines for the context of physcraper
    - [x] they do database wide homology search
    - [ ] they forget about original alignments
    - [x] do they take into account homology?
    - [x] how pipelines are crucial to fulfill the phylogenetically informative potential of GenBank.
    - [ ] but why have they failed
